Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2021-03-11 A-BasicCommom/ICCV2021/iccv_apsp.tex
1. ICCV2021 I am coming~

% This version of CVPR template is provided by Ming-Ming Cheng.
% Please leave an issue if you found a bug:
% https://github.com/MCG-NKU/CVPR_Template.

\documentclass[review]{cvpr}
%\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{297} % \times \times \times  Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  For the calculation of the all-pairs nodes shortest path in networks,
  Alon \etal proposed an efficient algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication,
  the all-pairs shortest path algorithm has lower time-bound of $O(14n^3)$.
  The proposed algorithm leverages the following improvements:
  matrix sparseness judgment, convergence judgment, distance product by matrix multiplication, association law for distance product,
  scale-free characteristics of the social networks degrees and the precision limit of floating point operations on the modern hardware.
  Comparing to Alon \etal's algorithm, the algorithm has improvement of 39\% on CPU and improvement of 36.2 times on GPU
  on the Chinese Movie Celebrity Network $2011\sim2015$ dataset.
\end{abstract}

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{11047} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi

@@

\maketitle
% Remove page # from the first page of camera-ready.
\ificcvfinal\thispagestyle{empty}\fi

%%%%%%%%% ABSTRACT
\begin{abstract}

  For the calculation of the all-pairs nodes shortest path in networks,
  Alon \etal proposed an efficient algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication,
  the all-pairs shortest path algorithm has lower time-bound of $O(14n^3)$.
  The proposed algorithm leverages the following improvements:
  matrix sparseness judgment, convergence judgment, distance product by matrix multiplication, association law for distance product,
  scale-free characteristics of the social networks degrees and the precision limit of floating point operations on the modern hardware.
  Comparing to Alon \etal's algorithm, the algorithm has improvement of 39\% on CPU and improvement of 36.2 times on GPU
  on the Chinese Movie Celebrity Network $2011\sim2015$ dataset.

\end{abstract}

### 2021-03-11 A-BasicCommom/ICCV2021/iccv_classification.tex
1. ICCV2021 I am coming~

% This version of CVPR template is provided by Ming-Ming Cheng.
% Please leave an issue if you found a bug:
% https://github.com/MCG-NKU/CVPR_Template.

\documentclass[review]{cvpr}
%\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{310} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

\maketitle

@@

  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
  As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

  Unsupervised pre-training is important to modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016,
  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
  thus, can be omitted in some cases.
  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  The pre-training process becomes one of the most important procedures in deep learning.

@@

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
which was inspired by unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
 ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.

@@

Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
Lu and Weng found that, for per-pixel approach, non-parametric classifiers, \eg neural networks, support vector machines, and decision trees,
are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
Fern{\'a}ndez \etal~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.

@@

My approach consists of a pre-training stage followed by a fine-tuning stage.
In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.

@@

@@

From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

@@

@@

\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
the metadata, which is the filename in this case, to the image class, which makes it is unfair to compare the performance with other image classification models.
Thus, to be more objective and fair, I add a preprocess step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
ASCII character of the filename then feeds into the model to do the inference.

@@

@@

{\small
\bibliographystyle{ieee_fullname}
%\bibliography{cpvr_classification}
\begin{thebibliography}{10}

  \bibitem{lee2009convolutional}
Lee, H., Grosse, R., Ranganath, R. \&  Ng, A.~Y.
\newblock {Convolutional deep belief networks for scalable unsupervised
  learning of hierarchical representations}.
\newblock In {\em Proceedings of the 26th annual international conference on
  machine learning}, pages 609--616, 2009.

\bibitem{nair2010rectified}
Nair, V. \&  Hinton, G.~E.
\newblock {Rectified linear units improve restricted boltzmann machines}.
\newblock In {\em ICML}, 2010.

\bibitem{mikolov2013distributed}
Mikolov, T., Sutskever, I., Chen, K., Corrado, G.~S. \&  Dean, J.
\newblock {Distributed representations of words and phrases and their
  compositionality}.
\newblock In {\em Advances in neural information processing systems}, pages
  3111--3119, 2013.

\bibitem{devlin2019bert}
Devlin, J., Chang, M.-W., Lee, K. \&  Toutanova, K.
\newblock {BERT: Pre-training of Deep Bidirectional Transformers for Language
  Understanding}.
\newblock In {\em NAACL-HLT (1)}, 2019.

\bibitem{vincent2008extracting}
Vincent, P., Larochelle, H., Bengio, Y. \&  Manzagol, P.-A.
\newblock {Extracting and composing robust features with denoising
  autoencoders}.
\newblock In {\em Proceedings of the 25th international conference on Machine
  learning}, pages 1096--1103, 2008.

\bibitem{chen2020generative}
Chen, M., Radford, A., Child, R., Wu, J., Jun, H., Dhariwal, P., Luan, D.
 and Sutskever, I.
\newblock {Generative Pretraining from Pixels}.
\newblock In {\em Proceedings of the 37th International Conference on Machine
  Learning}, 2020.

\bibitem{wang2019development}
Wang, W., Yang, Y., Wang, X., Wang, W. \&  Li, J.
\newblock {Development of convolutional neural network and its application in
  image classification: a survey}.
\newblock {\em Optical Engineering}, 58(4):40901, 2019.

\bibitem{lecun1990handwritten}
LeCun, Y., Boser, B.~E., Denker, J.~S., Henderson, D., Howard, R.~E., Hubbard,
  W.~E. \&  Jackel, L.~D.
\newblock {Handwritten digit recognition with a back-propagation network}.
\newblock In {\em Advances in neural information processing systems}, pages
  396--404, 1990.

\bibitem{krizhevsky2012imagenet}
Krizhevsky, A., Sutskever, I. \&  Hinton, G.~E.
\newblock {Imagenet classification with deep convolutional neural networks}.
\newblock In {\em Advances in neural information processing systems}, pages
  1097--1105, 2012.

\bibitem{zeiler2014visualizing}
Zeiler, M.~D. \&  Fergus, R.
\newblock {Visualizing and understanding convolutional networks}.
\newblock In {\em European conference on computer vision}, pages 818--833.
  Springer, 2014.

\bibitem{simonyan2014very}
Simonyan, K. \&  Zisserman, A.
\newblock {Very deep convolutional networks for large-scale image recognition}.
\newblock In {\em 3rd International Conference on Learning Representations,
  ICLR 2015 - Conference Track Proceedings}, San Diego, CA, United states,
  2015.

\bibitem{szegedy2015going}
Szegedy, C., Liu, W., Jia, Y., Sermanet, P., Reed, S., Anguelov, D., Erhan, D.,
  Vanhoucke, V. \&  Rabinovich, A.
\newblock {Going deeper with convolutions}.
\newblock In {\em Proceedings of the IEEE conference on computer vision and
  pattern recognition}, pages 1--9, 2015.

\bibitem{he2016deep}
He, K., Zhang, X., Ren, S. \&  Sun, J.
\newblock {Deep residual learning for image recognition}.
\newblock In {\em Proceedings of the IEEE conference on computer vision and
  pattern recognition}, pages 770--778, 2016.

\bibitem{xie2017aggregated}
Xie, S., Girshick, R., Doll{\'{a}}r, P., Tu, Z. \&  He, K.
\newblock {Aggregated residual transformations for deep neural networks}.
\newblock In {\em Proceedings of the IEEE conference on computer vision and
  pattern recognition}, pages 1492--1500, 2017.

\bibitem{szegedy2016inception}
Szegedy, C., Ioffe, S., Vanhoucke, V. \&  Alemi, A.~A.
\newblock {Inception-v4, inception-ResNet and the impact of residual
  connections on learning}.
\newblock In {\em 31st AAAI Conference on Artificial Intelligence, AAAI 2017},
  pages 4278--4284, San Francisco, CA, United states, 2017.

\bibitem{huang2016deep}
Huang, G., Sun, Y., Liu, Z., Sedra, D. \&  Weinberger, K.~Q.
\newblock {Deep networks with stochastic depth}.
\newblock In {\em European conference on computer vision}, pages 646--661.
  Springer, 2016.

\bibitem{lu2007survey}
Lu, D. \&  Weng, Q.
\newblock {A survey of image classification methods and techniques for
  improving classification performance}.
\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.

\bibitem{cui2020revisiting}
Cui, Y., Che, W., Liu, T., Qin, B., Wang, S. \&  Hu, G.
\newblock {Revisiting Pre-Trained Models for Chinese Natural Language
  Processing}.
\newblock In {\em Findings of EMNLP}. Association for Computational
  Linguistics, 2020.

\bibitem{he2017fine}
He, X. \&  Peng, Y.
\newblock {Fine-grained image classification via combining vision and
  language}.
\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
  Pattern Recognition}, pages 5994--6002, 2017.

\bibitem{reed2016learning}
Reed, S., Akata, Z., Lee, H. \&  Schiele, B.
\newblock {Learning deep representations of fine-grained visual descriptions}.
\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
  Pattern Recognition}, pages 49--58, 2016.

\bibitem{fernandez2014we}
Fern{\'{a}}ndez-Delgado, M., Cernadas, E., Barro, S. \&  Amorim, D.
  Amorim.
\newblock {Do we need hundreds of classifiers to solve real world
  classification problems?}
\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
  2014.

\bibitem{kim2014convolutional}
Kim, Y.
\newblock {Convolutional neural networks for sentence classification}.
\newblock In {\em EMNLP 2014 - 2014 Conference on Empirical Methods in Natural
  Language Processing, Proceedings of the Conference}, pages 1746--1751, Doha,
  Qatar, 2014.

\end{thebibliography}
}

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{11033} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi

@@

\maketitle
% Remove page # from the first page of camera-ready.
\ificcvfinal\thispagestyle{empty}\fi

@@

  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
  As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the ResNet model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

  Convolutional neural networks have achieved dominant performance in vision tasks for the rich representation for images.
  The LeNet architecture has been proved efficient than the Feed forward networks, and the Residual-style Networks have become popular recent years.
  VGGNet, ResNet, GoogLeNet showed that the depth, width are important factors for networks.
  Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.

  In the natural language processing domain, unsupervised pre-training becomes popular for the gigantic data collected by the industrial production.
  It started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Vaswani \etal~\cite{vaswani2017attention} used the Attention layers in the language translation task, and showed that the Attention layer overcome the drawback of the Recurrent Neural Networks
in parallel training. Devin \etal~\cite{devlin2019bert} employed the Transformer model, which take part of the Vaswani's Attention model and used Gigantic corpus in the pre-training phase, dominates in almost all natural language processing tasks in recent years.

  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009, and later from 2010 to 2016,
  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks.

  Some works use the Transformer networks in the image pixel pre-training, and use the model to generate image pixels.

@@

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
which was inspired by unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
 ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
  Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
Lu and Weng found that, for per-pixel approach, non-parametric classifiers, \eg neural networks, support vector machines, and decision trees,
are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
Fern{\'a}ndez \etal~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.

@@

@@

My approach consists of a pre-training stage followed by a fine-tuning stage.
In pre-training, I use BERT objectives, and the sequence Transformer architecture to predict language tokens.

@@

\subsection{The Chinese Pre-trained Transformer Language model}

\par The Transformer model is intended to be used as replacement of CNN layers for extracting information from Images.
Here, I describe how to train the Transformer language model in detail.

\subsection{The Chinese Word Piece Tokenization Model}

\par The BERT model use a tokenization method, named WordPiece, which breaks down a English word by high frequent suffix and prefix.
The vocabulary size can be greatly reduced by the sharing suffix and prefix between words.
Before training the custom WorkPiece model, the final vocabulary size and minimal word-piece frequency need to be assigned.
I use 21128 as the model vocabulary size and add several model specific tokens like $[PAD]$, $[UNK]$, $[MASK]$ used by the BERT model.

\subsection{The Chinese Pre-trained Transformer Language model}

@@

From Table (1), by combining the pre-trained language model with a fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

@@

%-------------------------------------------------------------------------
\subsection{The Effectiveness of the Pre-training Language Model Pixel Encoder}

\par I design two experiments to show how the pre-training on the Transformer model impact the accuracy of the image classification model.
With the same model architecture, and the pixel encoding approach, I choose a pre-trained language model and a same architecture without any pre-training.
With the same hyper parameters for the training, tested on the CIFAR-10 dataset, the pre-trained Transformer model has an accuracy of ?\%.
The random initialized three-layer-transformer model have achieved 26.85\% of accuracy on the CIFAR-10 test dataset, comparing to the accuracy of 40.63\% achieved by the
pre-trained transformer model with same architecture. 13.78\% is a significant improvement with the 4.5 billion tokens of Chinese language, it shows that with the unsupervised
training preprocess, the image classification accuracy can be greatly improved.

\subsection{Supervised Learning with Filenames}

\par I design two experiments to show if use the image class tag name during the training improve the performance or not.
The filename is the image classification information which represents the English name of the image object.

The encoded filename information randomly replace the image pixels and then feed to the transformer models.
However, with the filename information, the model performance has dropped by 0.51\% comparing to the pixels' information only.

Experiments showed that, the supervised filename rarely has positive impact on the performance of the classification model.

@@

\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
the metadata, which is the filename in this case, to the image classes, which makes it is unfair to compare the performance with other image classification models.
Thus, to be more objective and fair, I add a preprocessing step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
ASCII character of the filename then feeds into the model to do the inference.

Experiments show that the class tag information has improved the accuracy of ?\% on the CIFAR-10 dataset.

@@

\subsection{Multi-head Attention based ResNet model}

A vision system is an Attention mechanism that focuses limited attention on the key information, saving resources and getting the most efficient information quickly.
Attention models are less complex and have fewer parameters than CNN and RNN. So the demand for calculation is even smaller.
Attention addresses an issue in which RNN cannot be calculated in parallel.
The Attention mechanism does not rely on the calculations of the next step, so it can be processed in parallel with CNN.
Before the introduction of the Attention mechanism, there was a problem that long distances of information would be weakened,
just as people with weak memory could not remember the past.

\par RESNET has been proved to be efficient and effective in Computer Vision modeling, thus, a lot of time could be saved by supervised learning on a new CV task.
It is not surprising that the residual mechanism can learn deep layers with some layers skipped for different tasks.

\par I use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
The Attention has multiple heads and use the Self-Attention, the Query, Key, and Value dimensions are all same, 512 is an empirical value.

\par I use the Jittor library as the modeling tool, and the TsinghuaDog dataset to compare the performance with competitors.

\begin{table}
\begin{center}
\begin{tabular}{|l|r|}
\hline
Model   & Accuracy \\
\hline\hline
Attention-RESNET152 &  	78.29\% \\
RESNET152  	&	85.14\% \\
SE-RESNET152  	&	83.34\% \\
\hline
DENSENET121   	&	75.29\% \\
shufflenet\_v2\_x0\_5  &	45.38\% \\
\hline
mobilenet\_v2 & 63.65\%\\
GoogLeNet & 68.84\%\\
Alexnet & 41.73\%\\
\hline
SE-RESNET50 & 79.47\% \\
RESNET50 & 72.64\%\\

\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the Attention-RESNET model.}
\end{table}

@@

{\small
\bibliographystyle{ieee_fullname}
\bibliography{iccv_classification}
}
